### 2023-05-01 ARB/standards/work-in-progress/document/tex/standard/foreword.tex
some standard formatting work

This standard provides an unambiguous definition of the programming
language Rexx. Its purpose is to facilitate portability of Rexx programs
for use on a wide variety of computer systems. History The computer
programming language Rexx was designed by Mike Cowlishaw to satisfy the
following principal aims: - to provide a highly readable command
programming language for the benefit of programmers and program readers,
users and maintainers; - to incorporate within this language program
design features such as natural data typing and control structures which
would contribute to rapid, efficient and accurate program development; -
to define a language whose implementations could be both reliable and
efficient on a wide variety of computing platforms.

>>>>

This standard provides an unambiguous definition of the programming
language Rexx. Its purpose is to facilitate portability of Rexx programs
for use on a wide variety of computer systems. History The computer
programming language Rexx was designed by Mike Cowlishaw to satisfy the
following principal aims:

\begin{itemize}
\item
  to provide a highly readable command programming language for the
  benefit of programmers and program readers, users and maintainers;
\item
  to incorporate within this language program design features such as
  natural data typing and control structures which would contribute to
  rapid, efficient and accurate program development;
\item
  to define a language whose implementations could be both reliable and
  efficient on a wide variety of computing platforms.
\end{itemize}
